---
title: "Entrega 5"
output: html_document
date: "2024-04-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Entrega 5

## Introducción 

## Construcción del portafolio
Para fines de esta entrega, se trabajará con un portafolio conformado únicamente de 2 acciones: FEMSA, al ser el activo principal del proyecto completo, y CEMEX, al ser una acción que también cotiza en la BMV. En este caso, el portafolio estará conformado por 200 acciones, divididas en partes iguales entre ambos activos. 
```{r}
library(PerformanceAnalytics)
library(quantmod)
library(tidyverse)
clave1 <- "FEMSAUBD.MX"
clave2 <- "CEMEXCPO.MX"
datos <- new.env()
getSymbols(c(clave1, clave2), from="2000-01-03",to = "2024-04-25", env=datos)
p1 <-datos[[clave1]][,6]
p2 <-datos[[clave2]][,6]
precios <- na.omit(merge.xts(p1,p2))
```

Para poder realizar los cálculos necesarios posteriores, se calcula el valor inicial del portafolio. 
```{r}
v0<-as.numeric(100*last(precios[,1]) + 100*last(precios[,2]))
v0
```

Tomando como apoyo la fórmula, se calcula la volatilidad del portafolio. 
$$\sigma=\sqrt{wCw^T}$$

```{r}
w <- c(100*as.numeric(last(precios[,1]))/v0,100*as.numeric(last(precios[,2]))/v0)
w
```
## VaR paramétrico
1,5,10 and 20 days
In the case of parametric estimation, you must use the value of the average daily volatility of the last six months and the value of “So”, will be the one to which the methodology is applied in class.


### Back testing
Do the Back testing for one day VaR with both methodology 

## VaR no paramétrico
1,5,10 and 20 days.
In the case of the non-parametric methodology, the student must use historical simulation (with all possible data and the So value of the day the methodology is applied in class).

### Gráfica
At the case of non-parametric estimation, the corresponding graph must be presented where the one-day VaR can be seen at the three estimated confidence levels 

### Back testing
Do the Back testing for one day VaR with both methodology 

## Composición óptima del portafolio
Find the optimal composition of the portfolio that minimizes the Value at Risk.