---
title: "Homework 3"
output: html_document
date: "2024-02-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 - A company’s cash position, measured in millions of dollars, follows a generalized. Wiener process with a drift rate of 0.5 per quarter and a variance rate of 4.0 per quarter. How high does the company’s initial cash position have to be for the company to have a less than 5% chance of a negative cash position by the end of 1 year?

### 1.1 Identify a and b for the generalized Wiener Process
a = 0.5 per quarter
b = √4 = 2 per quarter

### 1.2 Write the equation dx using a and b
dx = 0.5dt + 2dW
dx = 2dt + 2ε√dt  Cambios por trimestre

### 1.3 Write the equation dx when dt=4 (fourth quarters or one year)
dx = 2 + 4ε Cambios por año 

### 1.4 Suppose that the initial cash position is Xo. Write the equation for X (not for dx)
x = x0 + dx
x = x0 + 2 + 4ε  Efectivo total en un año

### 1.5 Find the expected value and variance of X
E[x] = E[xo] + E[2] + E[4ε] = x0 + 2 + 0 = x0 + 2
Var[x] = Var[x0] + Var[2] + Var[4ε] = 0 +0+ 16(1) = 16

### 1.6 Using 5) find P(X<0). Normalize and use normal standard distribution. If you are doing good, you should get a result that depends on Xo. Now your job is to find this value
x~N(x0+2,16)
P(X<0) = P(z < (0-(x0+2)/√16) = P(z < (-x0-2)/4)

### 1.7 Equalize de result on 6) to -1.65 (because you want less than 5% chance of a negative position). And solve for Xo.
z0 = (-x0-2)/4 = -1.65 (este valor se busca en la tabla en caso de que no sea proporcionado)
-x0 -2 = -6.60
-x0 = -4.60
x0 = 4.60

### 1.8 Use R to prove your answer. Simulate the equation X=Xo+adt+bdW using the Xo you found on 7) with dt=4 and a,b for the problem. Once you have at least 10000 simulations for X, calculate its mean and variance. Finally, use pnorm(0, mean(X), sd(X)) to find the probability that X (initial cash position) has to be less than zero. 

```{r}

```


## 2 - A company’s cash position, measured in millions of dollars, follows a generalized Wiener process with a drift rate of 0.1 per month and a variance rate of 0.16 per month. The initial cash position is 2.0.
a = 0.1 per month
b = √.16 = 0.4 per month
x0 = 2

dx = 0.1dt + 0.4dW
dx = 0.12dt + 0.4ε√dt  Cambios por mes

dx = 0.12 + 0.4√12ε Cambios por año 

x = x0 + dx
x = 2 + 0.12 + 0.4√12ε  Efectivo total en un año

E[x] = E[2] + E[0.12] + E[0.4√12ε] = 2 + 0.12 + 0 = 2.12
Var[x] = Var[2] + Var[0.12] + Var[0.4√12ε ] = 0 +0+  = 



### 2.1 What are the probability distributions of the cash position after 1 month, 6 months, and 1 year?

### 2.2 What are the probabilities of a negative cash position at the end of 6 months and 1 year?

### 2.3 Use R to simulate the process and make a graph where you can see the relation between t form 1 to 40 months and the evolution of the probability 


