---
title: "Homework 3"
output: html_document
date: "2024-02-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 - A company’s cash position, measured in millions of dollars, follows a generalized. Wiener process with a drift rate of 0.5 per quarter and a variance rate of 4.0 per quarter. How high does the company’s initial cash position have to be for the company to have a less than 5% chance of a negative cash position by the end of 1 year?

### 1.1 Identify a and b for the generalized Wiener Process
a = 0.5 per quarter
b = √4 = 2 per quarter

### 1.2 Write the equation dx using a and b
dx = 0.5dt + 2dW
dx = 2dt + 2ε√dt  Cambios por trimestre

### 1.3 Write the equation dx when dt=4 (fourth quarters or one year)
dx = 2 + 4ε Cambios por año 

### 1.4 Suppose that the initial cash position is Xo. Write the equation for X (not for dx)
x = x0 + dx
x = x0 + 2 + 4ε  Efectivo total en un año

### 1.5 Find the expected value and variance of X
E[x] = E[xo] + E[2] + E[4ε] = x0 + 2 + 0 = x0 + 2
Var[x] = Var[x0] + Var[2] + Var[4ε] = 0 +0+ 16(1) = 16

### 1.6 Using 5) find P(X<0). Normalize and use normal standard distribution. If you are doing good, you should get a result that depends on Xo. Now your job is to find this value
x~N(x0+2,16)
P(X<0) = P(z < (0-(x0+2)/√16) = P(z < (-x0-2)/4)

### 1.7 Equalize de result on 6) to -1.65 (because you want less than 5% chance of a negative position). And solve for Xo.
z0 = (-x0-2)/4 = -1.65 (este valor se busca en la tabla en caso de que no sea proporcionado)
-x0 -2 = -6.60
-x0 = -4.60
x0 = 4.60

### 1.8 Use R to prove your answer. Simulate the equation X=Xo+adt+bdW using the Xo you found on 7) with dt=4 and a,b for the problem. Once you have at least 10000 simulations for X, calculate its mean and variance. Finally, use pnorm(0, mean(X), sd(X)) to find the probability that X (initial cash position) has to be less than zero. 


```{r}
set.seed(40)
n <- 100000
dt <- 4

a <- 0.5
b <- 2
x0 <- 4.6

epsilon <- rnorm(n, 0, 1)
dw <- epsilon*sqrt(dt) 
dX <- a*dt + b*dw
X <- x0 + dX

mean(X)
sd(X)^2
```

```{r}
1  - pnorm(q=0, mean=mean(X), sd=sd(X), lower.tail=FALSE) 
```


## 2 - A company’s cash position, measured in millions of dollars, follows a generalized Wiener process with a drift rate of 0.1 per month and a variance rate of 0.16 per month. The initial cash position is 2.0.
a = 0.1 per month
b = √.16 = 0.4 per month
x0 = 2

dx = 0.1dt + 0.4dW
dx = 0.1dt + 0.4ε√dt  Cambios por mes

dx = 0.12 + 0.4√12ε Cambios por año 

x = x0 + dx
x = 2 + 0.12 + 0.4√12ε  Efectivo total en un año

E[x] = E[2] + E[0.12] + E[0.4√12ε] = 2 + 0.12 + 0 = 2.12
Var[x] = Var[2] + Var[0.12] + Var[0.4√12ε ] = 0 +0+  = 



### 2.1 What are the probability distributions of the cash position after 1 month, 6 months, and 1 year?

> A un mes

$$ X = 2 + 0.1dt + 0.4\epsilon\sqrt{dt} = 2 + 0.1(1) + 0.44\sqrt{1}\epsilon $$
$$ X = 2.1 + 0.4\epsilon $$
$$ E[X] = E[2.1] + 0.4E[\epsilon] = 2.1 $$
$$ Var[X] = Var[2.1] + Var[0.4\epsilon] = 0.16Var[\epsilon] = 0.16 $$
Entonces $ N ~ (2.1,0.16) $

> A seis meses

$$ X = 2 + 0.1dt + 0.4\epsilon\sqrt{dt} = 2 + 0.1(6) + 0.4\sqrt{6}\epsilon $$
$$ X = 2.6 + 0.4\sqrt{6}\epsilon $$
$$ E[X] = E[2.6] + 0.4\sqrt{6} E[\epsilon] = 2.6 $$
$$ Var[X] = Var[2.6] + Var[0.4\sqrt{6}\epsilon] = 0.96Var[\epsilon] = 0.96 $$
Entonces, cuando pasen seis meses la variable X tendrá una distribución $ N ~ (2.6,\sqrt{0.96}) $

> A un año

$$ X = 2 + 0.1dt + 0.4\epsilon\sqrt{dt} = 2 + 0.1(12) + 0.4\sqrt{12}\epsilon $$
$$ X = 3.2 + 0.4\sqrt{12}\epsilon $$
$$ E[X] = E[3.2] + 0.4\sqrt{12} E[\epsilon] = E[3.2] + 0.4\sqrt{12}*0 = 3.2 $$
$$ Var[X] = Var[2.6] + Var[0.4\sqrt{12}\epsilon] = 192Var[\epsilon] = 1.92 $$
Entonces, a un año X tendrá una distribución $ N ~ (3.2,\sqrt{1.92}) $

### 2.2 What are the probabilities of a negative cash position at the end of 6 months and 1 year?

> At the end of six months

Standarizing the distribution $ Z = \frac{q-\mu}{\sigma} = \frac{0-2.6}{\sqrt{0.96}} = -2.6533 $

Finding the value of Z in Excel $P(X<0) = 0.003982$

> At the end of one year

Standarizing the distribution $ Z = \frac{q-\mu}{\sigma} = \frac{0-3.2}{\sqrt{1.92}} = -2.3094 $

Finding the value of Z in Excel $P(X<0) = 0.0104$

### 2.3 Use R to simulate the process and make a graph where you can see the relation between t form 1 to 40 months and the evolution of the probability 

```{r}
n <- 100000
dt <- 40

a <- 0.1
b <- 0.4
x0 <- 2

epsilon <- rnorm(n, 0, 1)
dw <- epsilon*sqrt(dt) 
dX <- a*dt + b*dw
X <- x0 + dX

mean(X)
sd(X)^2

```

```{r}
# Simular para graficar los dias
n <- 2000
dt <- 1
dias <- 40
a <- 0.1
b <- 0.4

X0 <- 2
X <- matrix(0, nrow=n, ncol=dias)

X[,1] <- X0

for (j in 1:n) {
epsilon <- rnorm(n,mean = 0, sd = 1)
dw <- epsilon*sqrt(dt)
dX <- a*dt + b*dw

for (t in 2:dias) {
    X[j,t] <- X[j,t-1] + dX[t]
}}

mean(X[,40])
sd(X[,40])^2
```

```{r}
# Graficar
X_graficar = colMeans(X)

plot(X_graficar, type="l")
```

```{r}
plot(X[31,], type='l')
```

